Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-01-31 Draft/scanNLO.tex
scanNLO: plots modifications and selection

{\bf GP: Comment on the other distributions: all the plots ?}
\begin{figure}[hbt]
\centering
{\includegraphics[scale=0.35]{figures/scanfigures/ptj1_nlo.pdf}}
{\includegraphics[scale=0.35]{figures/scanfigures/ptj2_nlo.pdf}}
\caption{NLO QCD inclusive study: $p_t$ distributions of the two leading jets, obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_2}
\end{figure}

\begin{figure}[hbt]
\centering
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/ptj3_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj2_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zmu_nlo.pdf}}
\caption{{\bf FIGURES STILL TO BE MODIFIED} } \label{fig:mjjdyjj_1d_3}
\end{figure}

>>>>

{\bf GP: Comment on the other distributions: all the plots ?}
\begin{figure}[hbt]
\centering 
{\includegraphics[scale=0.35]{figures/scanfigures/ptj1_nlo.pdf}}
{\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
\caption{NLO QCD inclusive study: transverse momentum and rapidity distributions of the leading jet, obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_2}
\end{figure}

\begin{figure}[hbt]
\centering
{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
\caption{NLO QCD inclusive study: distributions of the lepton--lepton invariant mass and the electron Zeppenfeld variable, obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_3}
\end{figure}
